Run PEER in each dataset

### 2020-11-18 combined_analysis/peer_in_each.Rmd
Initial commit

  cat(i, sum(idx), '\n')
  if( sum(idx) == 0){
    res = NULL
  }else{
    # normalize counts
    dge = DGEList( geneCountsMerged[isexpr,idx] )
    res = calcNormFactors(dge, "none")
  }
  res
})
names(dge.lst) = apply(grid, 1, paste, collapse=' - ')
dge.lst = dge.lst[!is.null(sapply(dge.lst, nrow))]

# form = ~ (1|Dx) + Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

@@

form = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3

@@

  # apply voom
  vobj = voomWithDreamWeights(dge[1:100,], form_use, info, save.plot=TRUE, BPPARAM = SnowParam(18))

>>>>

  cat(i, sum(idx), '\n')
  if( sum(idx) == 0){
    res = NULL
  }else{
    # normalize counts
    dge = DGEList( geneCountsMerged[isexpr,idx] )
    res = calcNormFactors(dge, "TMM")
  }
  res
})
names(dge.lst) = apply(grid, 1, paste, collapse=' - ')
dge.lst = dge.lst[!sapply(dge.lst, is.null)]

@@

@@

  # apply voom
  vobj = voomWithDreamWeights(dge, form_use, info, save.plot=TRUE, BPPARAM = SnowParam(18))
